Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-15 Grassmannian_cells.tex
typos + Thm 4.1

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition into affine spaces.  
  In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established. 
  We also provide two natural combinatorial labelings for these cells.
  On the one hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
  On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
  As there is a natural bijection between these two labelings, this also gives a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
\end{abstract}

@@

Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
it turns out that very interesting phenomena arise when restricting to certain quivers or to representations with certain properties.
For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
It has been conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.

@@

In this paper, we combine these two methods in order to show that every quiver Grassmannian attached to an exceptional representation of a generalized Kronecker quiver admits a cell decomposition into affine spaces.
The proof also shows that this is true for so-called truncated preprojective representations which appear as certain quotients of preprojective representations.
It turns out that these are precisely those representations which can be obtained from indecomposable representations with dimension vector $(d,1)$ when applying reflection functors.
Actually, we prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.

As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to a liftable representation of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
These are precisely those cases where the universal covering quiver differs from the original quiver.
This lifting property holds in particular for so-called tree modules, a class of representations which includes all exceptional representations.
The fixed point set of this torus action consists precisely of those subrepresentations which can also be lifted to the universal (abelian) covering quiver.
Actually, it turns out that each fixed point component is itself a quiver Grassmannian attached to the lifted representation.

The next step is to investigate conditions under which the fixed point components admit a cell decomposition.
Here the Caldero-Chapoton map comes into play.
In the case of the generalized Kronecker quiver, it turns out that a natural filtration of a fixed preprojective representation by preprojectives of smaller dimension transfers to the universal covering quiver.
These filtrations can be successively described by short exact sequences.
The main advantage when passing to the universal covering is that the preprojective representations covering the same dimension vector below become orthogonal, a property which rigidifies the situation in a sense.
In the end, this machinery can be used to recursively build cell decompositions of all quiver Grassmannians of lifted (truncated) preprojective representations.
As all the quiver Grassmannians of the (non-lifted) representation are smooth, this combines with the torus action to give a cell decomposition of these quiver Grassmannians.

@@

The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the Caldero-Chapoton map for short exact sequences of representations.
Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
\begin{thm}
  Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding $\CC^*$-action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{thm}
This torus action can be iterated in such a way that the remaining torus fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.
In view of results of Bia\l{}ynicki-Birula~\cite{bb} -- which roughly speaking yields that cell decompositions are preserved when passing from the fixed point components to the original variety -- we can use this result to lift the investigation of the geometry of quiver Grassmannians to the universal covering quiver.
This is important insofar as results such as Corollary~\ref{cor:perpendicular} are available which do not hold on the original quiver.
Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail and combining it with the torus method, we obtain the main result of this paper, see Theorems~\ref{cellscover} and~\ref{celldec}.
\begin{thm} 
  For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition into affine spaces.
\end{thm}
\noindent Note that, for $V=0$, we obtain the preprojective representations $P_{m+1}$.

In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions by introducing the notion of $2$-quivers which are a slight generalization of the usual notion of quivers.
Theorem \ref{thm:2quivercells} can be formulated as follows.
\begin{thm}
  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
  In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.
\end{thm}

@@

We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations.
Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
For $k\ge1$, set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
Depending on context (in particular, the parity of $m+1$ below), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(l)}$ for $1\le l<k$, these will not be naturally equipped with a canonical inclusion to $\tilde P_{m+1}$.

@@

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
\begin{theorem}
  \label{thm:bb}
  \cite[Section 4]{bb}
  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
Indeed, we can trivialize each affine bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$. As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
\begin{proposition} 
  \label{indecomposables}
  Let $m\geq 1$ and $d(m,r)=\udim P_{m+1}-r\udim P_m$ with $0\leq r\leq n-1$.
  The action of $\GL_n(\CC)$ is transitive on $\Ind\big(K(n),d(m,r)\big)$.
\end{proposition}
\begin{proof}
  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
  As the reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
  \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
    \Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}&\Ind\big(K(n),d(m+1,r)\big)}.\]
  As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}

@@

  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi_{m,I,j}^{-1}(V,W)$.
  This gives rise to the following commutative diagram:  
  \[\xymatrix{
    \Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
    0&0&0&}\]
  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
  This yields the isomorphisms
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W).\]

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(Z,\tilde K_m/W)\to\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is surjective.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
\end{proof}

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
  We establish the result for $m\ge2$ by proving the following more general statement:\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combinatorial Descriptions of Non-Empty Cells}
\label{sec:combinatorics}
\noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section~\ref{sec:fibrations}.
The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
We give a bijection between these which provides a partial geometric explanation for the combinatorial construction of counting polynomials for rank two quiver Grassmannians given in \cite{rupel}.

@@

  Finally, let $\beta\subset(Q_V)_0$ be strong sucessor closed in $\cQ_V$.
  Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
  To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\implies\{q\}$ for which the claim is obvious as above.
\end{proof}

@@

As an example consider the case $n=3$ and $m=3$. The $2$-quiver of $\tilde P_3$ is given by:\\

>>>>

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition into affine spaces.  
  In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established. 
  We also provide two natural combinatorial labelings for these cells.
  On the one hand, the cells are in bijection with compatible pairs in a maximal Dyck path as predicted by the theory of cluster algebras.
  On the other hand, they are labeled by certain subsets of a so-called $2$-quiver attached to a (truncated) preprojective representation.
  As there is a natural bijection between these two labelings this gives also a geometric explanation for the appearance of Dyck path combinatorics in the theory of quiver Grassmannians. 
\end{abstract}

@@

Although it follows from the results of Hille, Huisgen-Zimmermann and Reineke that every projective variety can be realized as a quiver Grassmannian, 
%-- which is maybe not surprising as the classification problem of indecomposable quiver representations is wild -- 
it turns out that very interesting phenomena arise when restricting to certain quivers or representations with certain properties.
For instance, quiver Grassmannians attached to exceptional representations are smooth \cite{cr}.
For tame quivers of types $\tilde A$ or $\tilde D$, it is known that every quiver Grassmannian attached to an indecomposable representation admits a cell decomposition into affine spaces, see \cite{ce,lw} and references therein.
It has been conjectured that this is also true for exceptional representations of any quiver, in particular for preprojective and preinjective representations.

@@

In this paper, we combine these two methods in order to show that every quiver Grassmannian attached to an exceptional representation of a generalized Kronecker quiver admits a cell decomposition into affine spaces.
The proof also shows that this is true for so-called truncated preprojective representations which appear as certain quotients of preprojective representations.
It turns out that these are precisely those representations which can be obtained from indecomposable representations with dimension vector $(d,1)$ when applying reflection functors.
Actually, we can prove that quiver Grassmannians of truncated preprojective representations only depend on the dimension vector of the representation itself and on the fixed dimension vector of the subrepresentations.

As a first step, we show that a torus action with proper fixed point set can be defined on any quiver Grassmannian attached to liftable representations of any acyclic quiver containing parallel arrows or non-oriented cycles, that is for representations which can be lifted to the universal (abelian) covering quiver.
These are precisely those cases where the universal covering quiver differs from the original quiver.
This lifting property holds in particular for so-called tree modules, a class of representations which includes all exceptional representations.
The fixed point set of this torus action consists precisely of those subrepresentations which can also be lifted to the universal (abelian) covering quiver.
Actually, it turns out that each fixed point component is itself a quiver Grassmannian attached to the lifted representation.

The next step is to investigate conditions under which the fixed point components admit a cell decomposition.
Here the Caldero-Chapoton map comes into play.
In the case of the generalized Kronecker quiver, it turns out that a natural filtration of a fixed preprojective representation by preprojectives of smaller dimension transfers to the universal covering quiver.
These filtration can be successively described by short exact sequences.
The main advantage when passing to the universal covering is that the preprojective representations covering the same dimension vector below become orthogonal, a property which rigidifies the situation in a sense.
In the end, this machinery can be used to recursively build cell decompositions of all quiver Grassmannians of lifted (truncated) preprojective representations.
As all the quiver Grassmannians of the (non-lifted) representation are smooth, this combines with the torus action to give a cell decomposition of these quiver Grassmannians.

@@

The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they all admit a cell decomposition into affine spaces.
This is obtained in Section~\ref{sec:fibrations} by combining a torus action on quiver Grassmannians which is introduced in Section~\ref{torusaction} and the so-called Caldero-Chapoton map for short exact sequences of representations.
Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
\begin{thm}
  Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding torus action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a torus action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{thm}
This torus action can be iterated in such a way that the remaining torus fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.
In view of results of Bia\l{}ynicki-Birula~\cite{bb} -- which roughly speaking yields that cell decompositions are preserved when passing from the fixed point components to the original variety -- we can use this result to lift the investigation of the geometry of quiver Grassmannians to the universal covering quiver.
This is important insofar as results such as Corollary~\ref{cor:perpendicular} are available which do not hold on the original quiver.
Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail and combining it with the torus method, we obtain the main result of this paper, see Theorems~\ref{cellscover} and~\ref{celldec}.
\begin{thm} 
  For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition into affine spaces.
\end{thm}
\noindent Note that, for $V=0$, we obtain the preprojective representations $P_{m+1}$.

In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions introducing the notion of $2$-quivers which is a slight generalization of the notion of usual quivers.
Theorem \ref{thm:2quivercells} can be formulated as follows.
\begin{thm}
  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
  In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.
\end{thm}

@@

We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations.
Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
For $k\ge1$, set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]%, i_j\ne i_{j+1}\text{ for $1\le j<l$}\}.\]
Depending on context (in particular, the parity of $m+1$), we will sometimes identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$.
In this way, to each word $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$ with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
Note that, although there is a translate of $\tilde P_{m+1-k}$ corresponding to each word $\ui\in A_1^{(l)}$ for $1\le l<k$, these will not be naturally equipped with a canonical inclusion to $\tilde P_{m+1}$.

@@

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points. The following is proved in \cite[Section 4]{bb}, see also \cite[Section 4]{ca}.
\begin{theorem}
  \label{thm:bb}
Let $X$ be a smooth projective complex variety with a $\C^\ast$-action.  Then each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine vector bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$ where we can choose an ordering such that $\coprod_{i=1}^s\Att(C_i)$ is closed for $1\leq s\leq r$.

  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

If each component $C_i$ admits a decomposition into affine spaces, Theorem~\ref{thm:bb} implies the same is true of $X$.
Indeed, we can trivialize each affine vector bundle $\Att(C_i)\to C_i$ over each affine piece of $C_i$ to get a decomposition of $X$ into affine spaces.

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
Write $\Ind\big(K(n),d\big)$ for the set of isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d$ for $d\in\NN^{K(n)_0}$. As the $\GL_n(\CC)$-action commutes with the natural base change action, we can define a $\GL_n(\CC)$-action on $\Ind\big(K(n),d\big)$.
\begin{proposition} 
  \label{indecomposables}
  Let $m\geq 1$ and $d(m,r)=\udim P_{m+1}-r\udim P_m$ with $0\leq r\leq n-1$.
  The action of $\GL_n(\CC)$ is transitive on $\Ind\big(K(n),d(m,r)\big)$.
\end{proposition}
\begin{proof}
  For $m=1$, the action of $\GL_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind\big(K(n),d(1,r)\big)$.
  As reflection functors preserve indecomposability and isomorphism classes, Lemma~\ref{compatibleGSigma} gives a commutative diagram as below for each $g\in\GL_n(\CC)$:
  \[\xymatrix{\Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}\ar[d]^{g^{-T}}&\Ind\big(K(n),d(m+1,r)\big)\ar[d]^g\\
    \Ind\big(K(n),d(m,r)\big)\ar[r]^(.45){\Sigma_2}&\Ind\big(K(n),d(m+1,r)\big)}.\]
  As the $\GL_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}

@@

  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi_{m,I,j}^{-1}(V,W)$.
  This gives rise to the following commutative diagram:  
  \[\xymatrix{
    0\ar[r] &\Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
    0\ar[r] &\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
    &0&0&0&}\]
  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
  This yields the isomorphisms
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W).\]

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is zero.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
\end{proof}

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
  We establish the result for $m\ge2$ by proving the following more general statement:\bigskip

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combinatorial description of non-empty cells}
\label{sec:combinatorics}
\noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section~\ref{sec:fibrations}.
The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
We give a bijection between these which provides a partial geometric explanation for the combinatorial construction of counting polynomials for rank two quiver Grassmannians given in \cite{rupel}.

@@

  Finally, let $\beta\subset(Q_V)_0$ be strong successor closed in $\cQ_V$.
  Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
  To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\implies\{q\}$ for which the claim is obvious as above.
\end{proof}

@@

As an example consider the case $n=3$ and $m=3$. The $2$-quiver of $\tilde P_3$ is given by:\bigskip
